An interactive environment for mapping computational structures to FPGAs

### 2016-07-06 paper/paper.tex
Worked on intro and added bib file and makefile.

  In this work-in-progress paper, we propose a more structural approach to computations.
  method..... math description to CSDF graph/ transformations to make efficient hardware then HW generation

  The current implementation: SDFkit, an interactive environment...

  Describe what is presented in remainder of paper..

\section{Approach}

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

@@

\section{Results}

@@

\section{Conclusion}

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
  \todo[inline]{extend conclusion a bit with current state of project}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

  In this work-in-progress paper, we propose a more structural approach to computations.
  As input, a mathematical description of the application is given which is transformed into a CSDF graph.
  Transformations to enhance performance are then applied to this graph.
  A cycle accurate simulation gives insight into where the bottlenecks of the application are.
  Finally, when the performance of the graph is sufficient, the graph is translated to hardware.

  As a proof of concept to show the effectiveness of the approach, an interactive environment for simulation and hardware generation  is being developed named SDFkit.
  Using SDFkit, CSDF graphs can be visualized and simulated in a cycle accurate manner.
  Additionally, using the code can be generated for FPGAs.

  The remainder of this paper is organized as follows:
  First, the approach is covered in Section \ref{sec:approach} after which results are covered in Section \ref{sec:results}.
  Finally, conclusion and future work are expressed in Section \ref{sec:conclusions}.

\section{Approach}
\label{sec:approach}

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse \cite{Wester15}}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert \cite{deGroote16}}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

@@

  \todo[inline]{mention CLaSH \cite{Baaij10} as used for backend}

\section{Results}
\label{sec:results}

@@

\section{Conclusions and future work}
\label{sec:conclusions}

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.

  \todo[inline]{extend conclusion a bit with current state of project}

  \todo[inline]{Future work: Complete support for CSDF, hierarchy is design environment, multicore and GPU code generation}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \begin{thebibliography}{1}

% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%   \bibliographystyle{unsrt}
% {\small\bibliography{biblio}}

% \end{thebibliography}

% bibliography{IEEEabrv,biblio}

\bibliographystyle{unsrt}
\bibliography{biblio}
